%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Siddharth Iyer} \\ \vspace{1pt}
    \small +1 437-243-4948 $|$ \href{mailto:x@x.com}{\underline{siyer2405@gmail.com}} $|$ 
    \href{https://linkedin.com/in/...}{\underline{www.linkedin.com/in/siyer2405}} $|$
    \href{https://github.com/...}{\underline{github.com/JigsawDragon}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Toronto}{Sept 2023 - June 2027}
      {Bachelor of Science -  Computer Science (Honours)}{Mississauga, ON}
    \resumeItemListStart
        \resumeItem{Relevant Courses: Data Structures and Algorithms, Computer Architecture, Software Design.}
    \resumeItemListEnd
    \resumeSubHeadingListEnd
%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
    \resumeSubheading
      {Full Stack Software Developer \textnormal{\emph{AngularJS, .NET Core, SSMS, Docker, Git}}}{ May 2025 -- August 2025}
      {Axiom Group Inc.}{Aurora, ON}
      \resumeItemListStart
        \resumeItem{Deployed and maintained new features used by over \textbf{200+ employees} in an \textbf{ERP system} (Prism).}
        \resumeItem{Migrated ERP from Angular v8 → v19, \textbf{cutting build times by over 20s} in live production environments.}
        \resumeItem{Maintained and scaled backend services using \textbf{Node.js, Docker}, and \textbf{SQL Server (SSMS)}.}
        \resumeItem{Communicated with team leads to scope out and deliver new ERP features in line with workflow requirements.}
        \resumeItem{Debugged and tested across multiple languages and frameworks, ensuring production stability.}
      \resumeItemListEnd
\resumeSubHeadingListEnd
%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Full Stack Task Tracker} $|$ \emph{AngularJS, SQL, .NET Core, EF Core, Docker}}{\href{https://github.com/JigsawDragon/task-tracker}{\underline{Project Link}}}
          \resumeItemListStart
            \resumeItem{Built a full-stack task tracker used by peers, enabling \textbf{100+} tasks tracked with realtime updates.}
            \resumeItem{Implemented a responsive and user-friendly interface using \textbf{AngularJS} for seamless task management.}
            \resumeItem{Created an \textbf{API using .NET Core and Entity Framework Core} to handle backend task operations.}
            \resumeItem{Containerized the application with \textbf{Docker}, ensuring consistent environments across development and production.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Pathway AI Tool} $|$ \emph{Next.js, HTML, CSS, Javascript, Typescript, OpenAI, Chromadb, Git}}{\href{https://github.com/49M/Pathway_App}{\underline{Project Link}}}
          \resumeItemListStart
            \resumeItem{Developed a tool collaboratively for course recommendations using \textbf{OpenAI prompts} and embeddings models.}
            \resumeItem{Used \textbf{Python web-scraping} with \textbf{BeautifulSoup} to scrape a university website for course information.}
            \resumeItem{Engineered prompts with a Chromadb embeddings model to align OpenAI responses with user queries.}
            \resumeItem{Improved efficiency by \textbf{reducing course search time} by an estimated \textbf{70\%} compared to manual browsing.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Dr.Mario in Assembly} $|$ \emph{Assembly, MIPS Architecture, }}{\href{https://github.com/JigsawDragon/dr-mario-assembly}{\underline{Project Link}}}
          \resumeItemListStart
            \resumeItem{Created a full functioning Dr.Mario game on Assembly with \textbf{MIPS} instruction set.Implemented complete Dr. Mario puzzle game mechanics in \textbf{MIPS} assembly language with \textbf{2000+ lines} of optimized code.}
            \resumeItem{Built fully functional \textbf{game physics} including pill rotation, gravity simulation, and chain reactions.}
            \resumeItem{Designed custom memory management system for game state, animations, and sounds within limited resources.}
            \resumeItem{Minimized memory footprint by implementing custom data structures and efficient \textbf{register allocation}.}

          \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{2D Pathfinder RPG} $|$ \emph{Unity, C\#, .NET Framework}}{\href{https://github.com/JigsawDragon/2DUnityRPG}{\underline{Project Link}}}
        \resumeItemListStart
          \resumeItem{Programmed a \textbf{custom pathfinding algorithm} based on complex templates.}
          \resumeItem{Developed character movement and collision mechanics using \textbf{Unity's Rigidbody2D and Physics System}.}
          \resumeItem{Utilized Unity’s \textbf{Tilemap Editor} to design interactive 2D environments with \textbf{layered assets}.}
         \resumeItemListEnd  
\resumeSubHeadingListEnd
  
%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Java, C\#, HTML, CSS, Javascript/Typescript, C/C++, Assembly, SQL} \\
     \textbf{Frameworks}{:  AngularJS, React, MSSQL, .NET, Flask, Linux} \\
     \textbf{Developer Tools}{: Node,js, Git, Vim, Visual Studio, Docker, Unity, Agile, NoSQL} \\

     }}
 \end{itemize}


%-------------------------------------------
\end{document}
